[dcpo_demsupport]

### 2020-06-25 paper/dcpo_demsupport.Rmd
clean up
incorporate cys_crosswalk into Rmd file (so that updates propagate automatically)

```{r claassen_input}
load("data/cys_crosswalk.RData")

@@

claassen_input <- DCPOtools::format_claassen(claassen_input_raw)
```

```{r claassen_m5, eval=FALSE}
claassen_m5 <- rstan::stan(file = 'R/argon/dcpo_demsupport/R/supdem.stan.mod5.stan',
                           data = claassen_input,
                           iter = 2000,
                           warmup = 1000,
                           chains = 4,
                           cores = 4,
                           thin = 2,
                           pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),
                           control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=15))

>>>>

```{r claassen_input}
supdem <- dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
    read_csv(col_types = "cdcddcdc")

supdem_cy <- supdem %>%                                             # 1390 obs
    janitor::clean_names() %>% 
    mutate(old_country = country,
           country = countrycode::countrycode(old_country, "country.name", "country.name")) %>%
    dplyr::select(country, year, project) %>% 
    unique()

claassen_input_cy <- read_csv("data/claassen_input_raw.csv",
                              col_types = "cdcddcd") %>%           # 1578 obs
    mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
           project = case_when(p_dcpo == "afrob" ~ "afb",
                               p_dcpo == "amb" ~ "lapop",
                               p_dcpo == "arabb" ~ "arb",
                               p_dcpo == "asiab" ~ "asb",
                               p_dcpo == "asianb" ~ "asnb",
                               p_dcpo == "neb" ~ "ndb",
                               p_dcpo == "sasianb" ~ "sab",
                               TRUE ~ p_dcpo),
           y_dcpo = year) %>%
    dplyr::select(country, year, y_dcpo, survey, project) %>% 
    unique()

no_problems <- inner_join(supdem_cy, claassen_input_cy)             # 1297 obs

needed <- anti_join(supdem_cy, claassen_input_cy)                   # 93 obs

available <- anti_join(claassen_input_cy, supdem_cy)                # 281 obs

year_fixes <- left_join(needed, available, by = c("country", "project")) %>% # 89 obs
    mutate(diff = year.x - year.y) %>% 
    group_by(country, project, year.x) %>% 
    mutate(closest_to_claassen = min(abs(diff))) %>% 
    ungroup() %>% 
    group_by(country, project, year.y) %>% 
    mutate(closest_to_dcpo = min(abs(diff))) %>% 
    ungroup() %>% 
    filter(closest_to_claassen == abs(diff) & closest_to_dcpo == abs(diff) & abs(diff) <= 3) %>% 
    filter(!(country == "Egypt" & year.x == 2014 & survey == "afrob5")) # double match (it's really afrob6)

cys_crosswalk <- year_fixes %>% 
    select(country, y_dcpo, y_claassen = year.x, survey)

missing_cyps <- anti_join(needed, year_fixes,  by = c("country", "year" = "year.x", "project")) # 4 obs; listed in issue #5

cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 192 obs
    select(-y_dcpo)

@@

claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
save(claassen_input, file = "data/claassen_input.Rda")
```

```{r claassen_m5, eval=FALSE}
claassen_m5 <- rstan::stan(file = 'R/argon/dcpo_demsupport/R/supdem.stan.mod5.stan',
                           data = claassen_input,
                           iter = 2000,
                           warmup = 1000,
                           chains = 4,
                           cores = 4,
                           thin = 2,
                           pars = c("mu_lambda", "sigma_lambda", "sigma_delta", "sigma_theta", "phi", "lambda", "delta", "theta", "x_pred","log_lik"),
                           control = list(adapt_delta=0.99, stepsize=0.02, max_treedepth=11))
